A Large-Scale Study of the Use of Eval in R

### 2020-08-23 inst/paper/main.tex
Fix table

In our corpus eval is called \AllAllCallCountRnd{} times out of \missingNumber
total calls to all R functions. This is merely \missingPercentage of the total
number of calls. \missingTable breaks down the number of calls and callsites for
the four kinds of eval functions from the three source; core R, packages and
Kaggle code.

\begin{tabular}{c|c|c|c|c|c}
  Function  & Core & Packages & Kaggle & All \\
  eval & \CoreEvalCallCountRnd & \PackageEvalCallCountRnd & \KaggleEvalCallCountRnd & \AllEvalCallCountRnd \\
  evalParent & \CoreEvalParentCallCountRnd & \PackageEvalParentCallCountRnd & \KaggleEvalParentCallCountRnd & \AllEvalParentCallCountRnd \\
  evalq & \CoreEvalqCallCountRnd & \PackageEvalqCallCountRnd & \KaggleEvalqCallCountRnd & \AllEvalqCallCountRnd \\
  local & \CoreLocalCallCountRnd & \PackageLocalCallCountRnd & \KaggleLocalCallCountRnd & \AllLocalCallCountRnd \\
  all & \CoreAllCallCountRnd & \PackageAllCallCountRnd & \KaggleAllCallCountRnd & \AllAllCallCountRnd
\end{tabular}

\begin{tabular}{c|c|c|c|c|c}
  Function  & Core & Packages & Kaggle & All \\
  eval & \CoreEvalSiteCountRnd & \PackageEvalSiteCountRnd & \KaggleEvalSiteCountRnd & \AllEvalSiteCountRnd \\
  evalParent & \CoreEvalParentSiteCountRnd & \PackageEvalParentSiteCountRnd & \KaggleEvalParentSiteCountRnd & \AllEvalParentSiteCountRnd \\
  evalq & \CoreEvalqSiteCountRnd & \PackageEvalqSiteCountRnd & \KaggleEvalqSiteCountRnd & \AllEvalqSiteCountRnd \\
  local & \CoreLocalSiteCountRnd & \PackageLocalSiteCountRnd & \KaggleLocalSiteCountRnd & \AllLocalSiteCountRnd \\
  all & \CoreAllSiteCountRnd & \PackageAllSiteCountRnd & \KaggleAllSiteCountRnd & \AllAllSiteCountRnd
\end{tabular}

The core R packages are the biggest consumers of eval. Majority of calls,
\CoreAllCallCountRnd, originate from the core R packages. Kaggle code, which is
end-user code, has merely \KaggleAllCallCountRnd calls to eval.

Of the \missingNumber packages in our corpus, only \missingNumber packages call
eval. \missingTable shows the number of calls to eval made by the ten most
frequent callers to eval. \missingNumber packages account for over
\missingPercentage calls to eval.

>>>>

In our corpus eval is called \AllAllCallCountRnd{} times out of \missingNumber
total calls to all R functions. This is merely \missingPercentage of the total
number of calls. Table \ref{table:eval-count-summary} shows the number of
calls and callsites for the four kinds of eval functions from core and packages.
The core R packages are the biggest consumers of eval. Majority of calls,
\CoreAllCallCountRnd, originate from the core R packages. Kaggle code, which is
end-user code, has merely \KaggleAllCallCountRnd calls to eval.

\begin{table}[ht]
  \resizebox{\columnwidth}{!}{%
    \begin{tabular}{l|rr|r||rr|r}
      \hline
      \multicolumn{1}{c}{Function}& \multicolumn{3}{c}{Calls} & \multicolumn{3}{c}{Callsites}\\
      \cline{1-1} \cline{2-4} \cline{5-7}
                                  & Core & Packages & Total & Core & Packages & Total\\
      \hline
      \c{eval} & \CoreEvalCallCountRnd & \PackageEvalCallCountRnd  & \AllEvalCallCountRnd & \CoreEvalSiteCountRnd & \PackageEvalSiteCountRnd &  \AllEvalSiteCountRnd\\
      \c{eval.parent} & \CoreEvalParentCallCountRnd & \PackageEvalParentCallCountRnd  & \AllEvalParentCallCountRnd & \CoreEvalParentSiteCountRnd & \PackageEvalParentSiteCountRnd & \AllEvalParentSiteCountRnd\\
      \c{evalq} & \CoreEvalqCallCountRnd & \PackageEvalqCallCountRnd  & \AllEvalqCallCountRnd & \CoreEvalqSiteCountRnd & \PackageEvalqSiteCountRnd & \AllEvalqSiteCountRnd \\
      \c{local} & \CoreLocalCallCountRnd & \PackageLocalCallCountRnd  & \AllLocalCallCountRnd & \CoreLocalSiteCountRnd & \PackageLocalSiteCountRnd & \AllLocalSiteCountRnd \\
      \hline
      Total & \CoreAllCallCountRnd & \PackageAllCallCountRnd  & \AllAllCallCountRnd & \CoreAllSiteCountRnd & \PackageAllSiteCountRnd & \AllAllSiteCountRnd \\
      \hline
    \end{tabular}
  }
  \label{table:eval-count-summary}
  \caption{Distribution of eval calls and callsites in the corpus}
\end{table}
